\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-27 paper.qmd
Added author's suggestion

## Introduction {#sec-intro}

@@

>>>>

@@

<!-- UMAP layout with author's suggested parameter choice-->
```{r}
#| warning: false
#| echo: false

## Import data
training_data_pbmc <- read_rds("data/pbmc3k/pbmc_pca_50.rds")
training_data_pbmc <- training_data_pbmc[, 1:9] |>
  mutate(ID = 1:NROW(training_data_pbmc))

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_30_min_dist_0.3.rds")
umap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = umap_pbmc, 
                                                                 x = "UMAP1", y = "UMAP2"))) |>
  dplyr::rename(c("UMAP1" = "scaled_UMAP1", 
                  "UMAP2" = "scaled_UMAP2")) |>
  dplyr::mutate(ID = 1:NROW(umap_pbmc))

umap_plot_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.5) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm')) 
```

```{r}
#| echo: false
#| fig-cap: "2D layout from UMAP (n_neighbors = 30, min_dist = 0.3) applied for the PBMC3k dataset. Is this a best representation of the original data?"
#| label: fig-umapauthor
#| fig-pos: H

umap_plot_pbmc 
```

### 2024-03-27 paper.tex
Added author's suggestion

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Looking at Non-Linear Dimension Reductions as Models in the Data Space},
  pdfauthor={Jayani P.G. Lakshika; Dianne Cook; Paul Harrison; Michael Lydeamore; Thiyanga S. Talagala},
  pdfkeywords={high-dimensional data, dimension
reduction, triangulation, hexagonal binning, low-dimensional
manifold, manifold learning, tour, data vizualization},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\section{Introduction}\label{sec-intro}

\begin{itemize}
\tightlist
\item
  What's the problem
\item
  Summary of literature
\end{itemize}

\section{Method}\label{method}

@@

\section{Applications}\label{applications}

\subsection{pbmc}\label{pbmc}

@@

\subsection{digits: 1}\label{digits-1}

@@

\section{Discussion}\label{discussion}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Looking at Non-Linear Dimension Reductions as Models in the Data Space},
  pdfauthor={Jayani P.G. Lakshika; Dianne Cook; Paul Harrison; Michael Lydeamore; Thiyanga S. Talagala},
  pdfkeywords={high-dimensional data, dimension
reduction, triangulation, hexagonal binning, low-dimensional
manifold, manifold learning, tour, data vizualization},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

\begin{itemize}
\tightlist
\item
  What's the problem:
\end{itemize}

Non-linear dimension reduction being used to summarise high-dimensional
data.

\begin{itemize}
\tightlist
\item
  Summary of literature
\end{itemize}

Relevant high-d vis, NLDR history

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/fig-umapauthor-1.pdf}

}

\caption{\label{fig-umapauthor}2D layout from UMAP (n\_neighbors = 30,
min\_dist = 0.3) applied for the PBMC3k dataset. Is this a best
representation of the original data?}

\end{figure}

\hypertarget{method}{%
\section{Method}\label{method}}

@@

\hypertarget{applications}{%
\section{Applications}\label{applications}}

\hypertarget{pbmc}{%
\subsection{pbmc}\label{pbmc}}

@@

\hypertarget{digits-1}{%
\subsection{digits: 1}\label{digits-1}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}
